quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-15 paper-quollr.tex
Develop the hexagonal binning code from scratch, write the main steps, write the shift fuction from the scratch as well

@@

\hypertarget{implementation}{%
\section{Implementation}\label{implementation}}

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

The package can be installed from CRAN using

\begin{quote}
\texttt{install.packages("quollr")}
\end{quote}

and from GitHub using

\begin{quote}
\texttt{remotes::install\_github("JayaniLakshika/quollr")}
\end{quote}

to install the development version.

\hypertarget{web-site}{%
\subsection{Web site}\label{web-site}}

More documentation of the package can be found at the web site (need to add the link).

\hypertarget{data-sets}{%
\subsection{Data sets}\label{data-sets}}

\hypertarget{functions}{%
\subsection{Functions}\label{functions}}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{verbatim}
#library(quollr)
library(readr)
library(ggplot2)
library(dplyr)
library(ggbeeswarm)
\end{verbatim}

@@

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{usage}{%
\subsection{Usage}\label{usage}}

\begin{itemize}
\tightlist
\item
  dependancies
\item
  basic example
\end{itemize}

@@

\begin{verbatim}
num_bins_x <- calculate_effective_x_bins(.data = s_curve_noise_umap, x = "UMAP1", cell_area = 1)
num_bins_x
\end{verbatim}

\begin{verbatim}
#> [1] 6
\end{verbatim}

\begin{verbatim}
shape_val <- calculate_effective_shape_value(.data = s_curve_noise_umap, x = "UMAP1", y = "UMAP2")
shape_val
\end{verbatim}

\begin{verbatim}
#> [1] 2.019414
\end{verbatim}

\begin{verbatim}
num_bins_y <- calculate_effective_y_bins(.data = s_curve_noise_umap, x = "UMAP2", y = "UMAP2", shape_val = 1.833091)
num_bins_y
\end{verbatim}

\begin{verbatim}
#> [1] 12
\end{verbatim}

@@

Generating full hexagonal grid contains main three steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Generate all the hexagonal bin centroids
\end{enumerate}

Steps:

\begin{itemize}
\tightlist
\item
  First compute hex grid bound values along the x and y axis and generate the all the points wthin the hex box
\end{itemize}

\begin{verbatim}
cell_area <- 1
cell_diameter <- sqrt(2 * cell_area / sqrt(3))

hex_size <- cell_diameter/2

buffer_size <- hex_size/2

x_bounds <- seq(min(s_curve_noise_umap[["UMAP1"]]) - buffer_size,
                  max(s_curve_noise_umap[["UMAP1"]]) + buffer_size, length.out = num_bins_x)

y_bounds <- seq(min(s_curve_noise_umap[["UMAP2"]]) - buffer_size,
                max(s_curve_noise_umap[["UMAP2"]]) + buffer_size, length.out = num_bins_y)

box_points <- expand.grid(x = x_bounds, y = y_bounds)

ggplot() +
  geom_point(data = box_points, aes(x = x, y = y), color = "red")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-5-1.pdf}

\begin{itemize}
\tightlist
\item
  Second for each x-value, find which y values are in the even row
\end{itemize}

\begin{verbatim}
 box_points <- box_points |>
    dplyr::arrange(x) |>
    dplyr::group_by(x) |>
    dplyr::group_modify(~ generate_even_y(.x)) |>
    tibble::as_tibble()

ggplot() +
  geom_point(data = box_points,
             aes(x = x, y = y, colour = as.factor(is_even)))
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-6-1.pdf}

\begin{itemize}
\tightlist
\item
  Then, shift the x values of the even rows
\end{itemize}

\begin{verbatim}
## Shift for even values in x-axis
x_shift <- unique(box_points$x)[2] - unique(box_points$x)[1]

box_points$x <- box_points$x + x_shift/2 * ifelse(box_points$is_even == 1, 1, 0)

ggplot() +
  geom_point(data = box_points, aes(x = x, y = y), color = "red")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-7-1.pdf}

\begin{verbatim}
all_centroids_df <- generate_full_grid_centroids(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y, 
                                                 buffer_size = NA, hex_size = NA)

glimpse(all_centroids_df)
\end{verbatim}

\begin{verbatim}
#> Rows: 72
#> Columns: 2
#> $ x <dbl> -3.5390002, -2.9126765, -3.5390002, -2.9126765, -3.5390002, -2.91267~
#> $ y <dbl> -6.0111830, -4.9111506, -3.8111182, -2.7110858, -1.6110534, -0.51102~
\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Generate hexagonal coordinates
\end{enumerate}

Steps:
- Compute horizontal width of the hexagon

\begin{itemize}
\item
  Compute vertical width of the hexagon and multiply by a factor for overlapping (\(sqrt(3) / 2 * 1.15\))
\item
  Obtain hexagon polygon coordinates
\item
  Obtain the number of hexagons in the full grid
\item
  Generate the coordinates for the hexagons
\end{itemize}

\begin{verbatim}
hex_grid <- gen_hex_coordinates(all_centroids_df)
glimpse(hex_grid)
\end{verbatim}

\begin{verbatim}
#> Rows: 432
#> Columns: 3
#> $ x  <dbl> -2.912676, -2.912676, -3.539000, -4.165324, -4.165324, -3.539000, -~
#> $ y  <dbl> -5.645998, -6.376368, -6.741553, -6.376368, -5.645998, -5.280813, -~
#> $ id <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4~
\end{verbatim}

\begin{verbatim}
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_point(data = all_centroids_df, aes(x = x, y = y), color = "red")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-10-1.pdf}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Map hexagonal IDs
\end{enumerate}

Steps:

\begin{itemize}
\item
  Filter the data set with specific y value
\item
  Order the x values for a specific y value
\item
  Repeat the process for all unique y values
\end{itemize}

\begin{verbatim}
full_grid_with_hexbin_id <- map_hexbin_id(all_centroids_df)

ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_text(data = full_grid_with_hexbin_id, aes(x = c_x, y = c_y, label = hexID))
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-11-1.pdf}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Map polygon IDs
\end{enumerate}

Steps:

\begin{itemize}
\item
  Filter specific hexagon
\item
  Filter specific polygon
\item
  Check the selected hexagonal centroid exists within the polygon
\item
  if so assign that id to centroid, if not check until find the polygon which contains the centroid
\end{itemize}

\begin{verbatim}
full_grid_with_polygon_id <- map_polygon_id(full_grid_with_hexbin_id, hex_grid)
\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Assign data into hexagons
\end{enumerate}

\begin{itemize}
\item
  Compute distances between nldr coordinates and hex bin centroids
\item
  Find the hexagonal centroid that have the minimum distance
\end{itemize}

\begin{verbatim}
s_curve_noise_umap_with_id <- assign_data(s_curve_noise_umap, full_grid_with_hexbin_id)
\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Compute standardized counts
\end{enumerate}

\begin{itemize}
\item
  Compute number of data points within each hexagon
\item
  Compute standardise count by dividing the counts by the maximum
\end{itemize}

\begin{verbatim}
df_with_std_counts <- compute_std_counts(nldr_df = s_curve_noise_umap_with_id)
\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  Extract full grid info
\end{enumerate}

\begin{itemize}
\item
  Assign standardize counts for hex bins
\item
  Join with the hexagonal coordinates
\end{itemize}

\begin{verbatim}
hex_full_count_df <- generate_full_grid_info(full_grid_with_polygon_id, df_with_std_counts, hex_grid)
\end{verbatim}

\begin{verbatim}
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_point(data = s_curve_noise_umap, aes(x = UMAP1, y = UMAP2), color = "blue")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-16-1.pdf}

\begin{verbatim}
ggplot(data = hex_full_count_df, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID)) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-17-1.pdf}

\hypertarget{buffer-size}{%
\paragraph{Buffer size}\label{buffer-size}}

When generating hexagonal bins in R, a buffer is often included to ensure that the data points are evenly distributed within the bins and to prevent edge effects. The buffer helps in two main ways:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Preventing Edge Effects}: Without a buffer, the outermost data points might fall near the boundary of the hexagonal grid, leading to incomplete bins or uneven distribution of data. By adding a buffer, you create a margin around the outer edges of the grid, ensuring that all data points are fully enclosed within the bins.
\item
  \textbf{Ensuring Even Distribution}: The buffer allows for a smoother transition between adjacent bins. This helps in cases where data points are not perfectly aligned with the grid lines, ensuring that each data point is assigned to the nearest bin without bias towards any specific direction.
\end{enumerate}

Overall, including a buffer when generating hexagonal bins helps to produce more accurate and robust binning results, particularly when dealing with real-world data that may have irregular distributions or boundary effects.

@@

\begin{verbatim}
## To generate a data set with high-D and 2D training data
df_all <- training_data |> dplyr::select(-ID) |>
  dplyr::bind_cols(s_curve_noise_umap_with_id)

## To generate averaged high-D data

df_bin <- avg_highD_data(.data = df_all, column_start_text = "x") ## Need to pass ID column name
\end{verbatim}

@@

\begin{verbatim}
df_bin_centroids <- hex_full_count_df[complete.cases(hex_full_count_df[["std_counts"]]), ] |>
  dplyr::select("c_x", "c_y", "hexID", "std_counts") |>
  dplyr::distinct() |>
  dplyr::rename(c("x" = "c_x", "y" = "c_y"))

df_bin_centroids
\end{verbatim}

\begin{verbatim}
#> # A tibble: 20 x 4
#>         x      y hexID std_counts
#>     <dbl>  <dbl> <int>      <dbl>
#>  1 -2.91  -4.91      7      0.5  
#>  2 -3.54  -3.81     13      0.5  
#>  3 -2.29  -6.01      2      0.5  
#>  4 -1.66  -4.91      8      0.75 
#>  5 -2.29  -3.81     14      0.5  
#>  6 -1.03  -3.81     15      0.375
#>  7 -0.407 -2.71     21      0.125
#>  8 -1.03  -1.61     27      0.125
#>  9  0.219 -1.61     28      1    
#> 10  0.845 -0.511    34      0.625
#> 11  0.845  1.69     46      0.125
#> 12  0.845  3.89     58      0.625
#> 13  0.219  4.99     64      0.125
#> 14  0.845  6.09     70      0.375
#> 15  1.47   0.589    41      1    
#> 16  1.47   2.79     53      0.125
#> 17  2.10   3.89     59      0.625
#> 18  1.47   4.99     65      0.5  
#> 19  2.10   6.09     71      0.375
#> 20  2.72   4.99     66      0.5
\end{verbatim}

\begin{verbatim}
tr1_object <- triangulate_bin_centroids(df_bin_centroids, x, y)
tr_from_to_df <- generate_edge_info(triangular_object = tr1_object)
\end{verbatim}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Assign shift along the x and y axis (limited the amount should less than the cell\_diameter)
\item
  Generate bounds with shift origin
\end{enumerate}

\begin{verbatim}
all_centroids_df_shift <- extract_coord_of_shifted_hex_grid(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y,
                                                 shift_x = 0.2690002, shift_y = 0.271183,
                                                 buffer_size = NA, hex_size = NA)

glimpse(all_centroids_df_shift)
\end{verbatim}

\begin{verbatim}
#> Rows: 72
#> Columns: 2
#> $ x <dbl> -3.2700000, -2.6436763, -3.2700000, -2.6436763, -3.2700000, -2.64367~
#> $ y <dbl> -5.7400000, -4.6399676, -3.5399352, -2.4399028, -1.3398704, -0.23983~
\end{verbatim}

\begin{verbatim}
hex_grid <- gen_hex_coordinates(all_centroids_df_shift)
glimpse(hex_grid)
\end{verbatim}

\begin{verbatim}
#> Rows: 432
#> Columns: 3
#> $ x  <dbl> -2.643676, -2.643676, -3.270000, -3.896324, -3.896324, -3.270000, -~
#> $ y  <dbl> -5.3748152, -6.1051848, -6.4703696, -6.1051848, -5.3748152, -5.0096~
#> $ id <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4~
\end{verbatim}

\begin{verbatim}
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_point(data = all_centroids_df_shift, aes(x = x, y = y), color = "red")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-23-1.pdf}

\begin{verbatim}
full_grid_with_hexbin_id <- map_hexbin_id(all_centroids_df_shift)

ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_text(data = full_grid_with_hexbin_id, aes(x = c_x, y = c_y, label = hexID))
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-24-1.pdf}

\begin{verbatim}
full_grid_with_polygon_id <- map_polygon_id(full_grid_with_hexbin_id, hex_grid)
\end{verbatim}

\begin{verbatim}
s_curve_noise_umap_with_id <- assign_data(s_curve_noise_umap, full_grid_with_hexbin_id)
\end{verbatim}

\begin{verbatim}
df_with_std_counts <- compute_std_counts(nldr_df = s_curve_noise_umap_with_id)
\end{verbatim}

\begin{verbatim}
hex_full_count_df <- generate_full_grid_info(full_grid_with_polygon_id, df_with_std_counts, hex_grid)
\end{verbatim}

\begin{verbatim}
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_point(data = s_curve_noise_umap, aes(x = UMAP1, y = UMAP2), color = "blue")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-29-1.pdf}

\begin{verbatim}
ggplot(data = hex_full_count_df, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID)) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff")
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-30-1.pdf}

\begin{verbatim}
df_bin_centroids <- hex_full_count_df[complete.cases(hex_full_count_df[["std_counts"]]), ] |>
  dplyr::select("c_x", "c_y", "hexID", "std_counts") |>
  dplyr::distinct() |>
  dplyr::rename(c("x" = "c_x", "y" = "c_y"))

df_bin_centroids
\end{verbatim}

\begin{verbatim}
#> # A tibble: 21 x 4
#>         x     y hexID std_counts
#>     <dbl> <dbl> <int>      <dbl>
#>  1 -3.27  -5.74     1      0.286
#>  2 -2.64  -4.64     7      0.571
#>  3 -3.27  -3.54    13      0.714
#>  4 -2.02  -5.74     2      0.857
#>  5 -1.39  -4.64     8      0.429
#>  6 -2.02  -3.54    14      0.286
#>  7 -0.765 -3.54    15      0.429
#>  8 -0.138 -2.44    21      0.143
#>  9 -0.765 -1.34    27      0.286
#> 10  0.488 -1.34    28      1    
#> # i 11 more rows
\end{verbatim}

\begin{verbatim}
tr1_object <- triangulate_bin_centroids(df_bin_centroids, x, y)
tr_from_to_df <- generate_edge_info(triangular_object = tr1_object)
\end{verbatim}

\begin{verbatim}
bin_centroids_shift <- ggplot(data = hex_full_count_df, aes(x = c_x, y = c_y)) +
  geom_point(color = "#bdbdbd") +
  geom_point(data = shifted_hex_coord_df, aes(x = c_x, y = c_y), color = "#feb24c") +
  coord_cartesian(xlim = c(-5, 8), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "a", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

hex_grid_shift <- ggplot(data = shifted_hex_coord_df, aes(x = x, y = y)) +
  geom_polygon(fill = NA, color = "#feb24c", aes(group = polygon_id)) +
  geom_polygon(data = hex_full_count_df, aes(x = x, y = y, group = polygon_id),
               fill = NA, color = "#bdbdbd") +
  coord_cartesian(xlim = c(-5, 8), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

## Before shift
before_shift_plot <- ggplot(data = hex_full_count_df, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID), size = 2) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  coord_equal() +
  theme_void() +
  theme(legend.position="bottom", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "a", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

## After shift
after_shift_plot <- ggplot(data = shifted_hex_coord_df, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_text(aes(x = c_x, y = c_y, label = hexID), size = 2) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  coord_equal() +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3) 
\end{verbatim}

@@

\begin{verbatim}
## Compute 2D distances
distance <- cal_2d_dist(.data = tr_from_to_df)

## To plot the distribution of distance
plot_dist <- function(distance_df){
  distance_df$group <- "1"
  dist_plot <- ggplot(distance_df, aes(x = group, y = distance)) +
    geom_quasirandom()+
    ylim(0, max(unlist(distance_df$distance))+ 0.5) + coord_flip()
  return(dist_plot)
}

plot_dist(distance)
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-34-1.pdf}

\begin{verbatim}
benchmark <- find_benchmark_value(.data = distance, distance_col = "distance")
\end{verbatim}

@@

\begin{verbatim}
trimesh <- ggplot(df_bin_centroids, aes(x = x, y = y)) +
  geom_point(size = 0.1) +
  geom_trimesh() +
  coord_equal()

trimesh
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-35-1.pdf}

@@

\begin{verbatim}
trimesh_gr <- colour_long_edges(.data = distance, benchmark_value = benchmark,
                                triangular_object = tr1_object, distance_col = distance)

trimesh_gr
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-36-1.pdf}

@@

\begin{verbatim}
trimesh_removed <- remove_long_edges(.data = distance, benchmark_value = benchmark,
                                     triangular_object = tr1_object, distance_col = distance)
trimesh_removed
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-37-1.pdf}

@@

\begin{verbatim}
tour1 <- show_langevitour(df_all, df_bin, df_bin_centroids, benchmark_value = benchmark,
                          distance = distance, distance_col = distance)
tour1
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-38-1.pdf}
